% This file was converted to LaTeX by Writer2LaTeX ver. 1.0.2
% see http://writer2latex.sourceforge.net for more info
\documentclass[a4paper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[french,english]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue, pdftitle=, pdfauthor=, pdfsubject=, pdfkeywords=}
% List styles
\newcommand\liststyleWWviiiNumi{%
\renewcommand\labelitemi{[F0B7?]}
\renewcommand\labelitemii{[F0B7?]}
\renewcommand\labelitemiii{[F0B7?]}
\renewcommand\labelitemiv{[F0B7?]}
}
\newcommand\liststyleWWviiiNumii{%
\renewcommand\labelitemi{[F0B7?]}
\renewcommand\labelitemii{[F0B7?]}
\renewcommand\labelitemiii{[F0B7?]}
\renewcommand\labelitemiv{[F0B7?]}
}
\newcommand\liststyleWWviiiNumiii{%
\renewcommand\labelitemi{[F0B7?]}
\renewcommand\labelitemii{[F0B7?]}
\renewcommand\labelitemiii{[F0B7?]}
\renewcommand\labelitemiv{[F0B7?]}
}
\newcommand\liststyleWWviiiNumiv{%
\renewcommand\labelitemi{[F0B7?]}
\renewcommand\labelitemii{[F0B7?]}
\renewcommand\labelitemiii{[F0B7?]}
\renewcommand\labelitemiv{[F0B7?]}
}
\newcommand\liststyleWWviiiNumv{%
\renewcommand\labelitemi{[F0B7?]}
\renewcommand\labelitemii{[F0B7?]}
\renewcommand\labelitemiii{[F0B7?]}
\renewcommand\labelitemiv{[F0B7?]}
}
% Page layout (geometry)
\setlength\voffset{-1in}
\setlength\hoffset{-1in}
\setlength\topmargin{0.7874in}
\setlength\oddsidemargin{0.7874in}
\setlength\textheight{10.118099in}
\setlength\textwidth{6.6932993in}
\setlength\footskip{0.0cm}
\setlength\headheight{0cm}
\setlength\headsep{0cm}
% Footnote rule
\setlength{\skip\footins}{0.0469in}
\renewcommand\footnoterule{\vspace*{-0.0071in}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.0071in}}\vspace*{0.0398in}}
% Pages styles
\makeatletter
\newcommand\ps@Standard{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{}
  \renewcommand\@oddfoot{}
  \renewcommand\@evenfoot{}
  \renewcommand\thepage{\arabic{page}}
}
\makeatother
\pagestyle{Standard}
\title{}
\author{}
\date{2015-03-11T04:25:58.947358726}
\begin{document}
{\bfseries
\ \ Explanations:}


\bigskip

\ \ In the HTTP part, we need to create an HTTP object which would allow
us to simulate a session. This object contains informations on the
different Random Generators used by HTTP model, the number of TCP
connection (burst mode or persistent), the parameters of an initial TCP
connection. So this object can be represented this way :


\bigskip

{\selectlanguage{english}
An HTTP page has for parameters \textbf{struct srcHTTPSS}:}


\begin{itemize}
\item randomGenerator SM : Size of the main object in a page
\end{itemize}
\begin{itemize}
\item randomGenerator Se : Size of an embedded object in a page
\end{itemize}
\begin{itemize}
\item randomGenerator Nd : Number of embedded objects in a page
\end{itemize}
\begin{itemize}
\item randomGenerator Dpc : Reading time
\end{itemize}
\begin{itemize}
\item randomGenerator Tp : Parsing time for the main page.
\item Int MTU
\item Int nbTCP : number of TCP connections according to the mode ( = 1
in persistant mode)
\item Int nbPage : number of page visited
\item {\selectlanguage{english}
boolean version : True si 1.1, false si 1.0}
\item struct srcHTTPSS\_t * src : source HTTP
\item void * destination : is a pointer to the destination entity for
TCP
\item processPDU\_t destProcessPDU : is the PDU processing function of
the destination
\item double RTTmd : is the Round Trip Time minus transmission time on
the access link
\item int initialWindow : is the initial value of cwnd
\item struct srcTCPSS\_t * srcTCP[4] : TCP sources for burst or
persitant mode, maximum 4 TCP sources
\item {\selectlanguage{french}
int nbTCPTermine : number of TCP connections which have endded in burst
mode}
\end{itemize}

\bigskip

{\selectlanguage{english}
First of all, we create a HTTP object by defining his parameters. This
following function will help us to perform this task.}

{\selectlanguage{english}\bfseries
struct srcHTTPSS\_t * srcHTTPSS\_init(struct randomGenerator\_t * Sm,}

{\selectlanguage{french}\bfseries
\ \ \ \ \ \ \ \ \ \ struct randomGenerator\_t * Se,}

{\selectlanguage{french}\bfseries
\ \ \ \ \ \ \ \ \ \ struct randomGenerator\_t * Nd,}

{\selectlanguage{french}\bfseries
\ \ \ \ \ \ \ \ \ \ struct randomGenerator\_t * Dpc,}

{\selectlanguage{french}\bfseries
\ \ \ \ \ \ \ \ \ \ struct randomGenerator\_t * Tp,}

{\selectlanguage{french}\bfseries
\ \ \ \ \ \ \ \ \ \ int MTU, int nbTCP, int version,}

{\selectlanguage{french}\bfseries
\ \ \ \ \ \ \ \ \ \ void * destination,}

{\selectlanguage{french}\bfseries
\ \ \ \ \ \ \ \ \ \ processPDU\_t destProcessPDU,}

{\selectlanguage{french}\bfseries
\ \ \ \ \ \ \ \ \ \ double RTTmd,}

{\selectlanguage{french}\bfseries
\ \ \ \ \ \ \ \ \ \ int initialWindow,}

{\selectlanguage{french}\bfseries
\ \ \ \ \ \ \ \ \ \ int nbPageMax)}


\bigskip

{\selectlanguage{english}
After having created the HTTP object, we can start the session by using
this following function:}

{\selectlanguage{english}\bfseries
\ \ void srcHTTPSS\_sessionStart(void * arg)}

{\selectlanguage{english}
\ \ The goal first aim of this function is to send via TCP the main
object. The parameter of this function is an void pointer, it will be
casted into an HTTP object : \textbf{struct srcHTTPSS\_t * src =
(struct srcHTTPSS\_t *) arg}.}

{\selectlanguage{english}
\ \ This function will be called at first, each time the simulator need
to upload a new page.}


\bigskip

{\selectlanguage{english}
\ \ Then we create a TCP source using the data of the parameter
\textbf{src}. Then the main object will be sent on this connection
newly created by using the function \textbf{void
srcTCPss\_sendFile(struct srcTCPSS\_t * src, int nbBytes)}. The
argument \textbf{nbBytes }size of the main object will be obtenaid via
the \textbf{getDoubleNext }of the Random Generators.}


\bigskip

{\selectlanguage{english}
\ \ Then we program an event indicating us the end of transmission of
the maine object. This event programming is made possible by the
function on the file event.c : \textbf{void event\_add(void (*run)(void
*data), void * data, motSimDate\_t date).}}


\bigskip

{\selectlanguage{english}
\ \ The moment when this event is launched, we would know that the main
object have been completely sent by the TCP connection. It will also
take us to this function : \textbf{void srcHTTPSS\_EOTMainObjet
(fonctionsHttpssArguments * arg).}}


\bigskip

{\selectlanguage{english}
\ \ In this function, we know that the main object have been totally
sent, so we need to simulate the parsing time. For performing that
task, we need to get the parsing time of \textbf{Tp }via
\textbf{getDoubleNext }\ of the Random Generator file. Then we create
the event end of parsing that will take place after \textbf{Tp }seconds
added to the current time.}

{\selectlanguage{french}
\ \ We use again the function \textbf{void event\_add(void (*run)(void
*data), void * data, motSimDate\_t date) }\ to create this event.}


\bigskip

{\selectlanguage{english}
\ \ At the end of the parsing, we can send the embedded objects. So the
end of parsing event will take us to this function : \textbf{void
srcHTTPSS\_sendEmbeddedObjects(fonctionsHttpssArguments * arg)}}

{\selectlanguage{english}
\ \ We will create \textbf{nbTCP }TCP connections according to the mode
(burst or persistent).}

{\selectlanguage{english}
\ \ We determine the number \textbf{Nd }\ of embedded objects by using
\textbf{getDoubleNext }of the random generators.}

{\selectlanguage{english}
\ \ We send the \textbf{Nd }embedded objects on the \textbf{nbTCP} TCP
connections by giving them also the size of the embedded objects.}

{\selectlanguage{english}
\ \ Then we create the event end of transmission of the embedded
objects.}

{\selectlanguage{english}
\ \ We have added also another function on TCP in order to wake up the
TCP connections which have finished too quickly before the event is
programmed.(it may happen when the size of objects are too small).}


\bigskip

{\selectlanguage{english}
\ \ When a TCP connection have finished his transmission, we will be
directed towards this function : \textbf{void
srcHTTPSS\_EOTEmbeddedObjects(fonctionsHttpssArguments * arg)}}

{\selectlanguage{english}
\ \ First in this function, we compute the number of TCP connection
which have passed through this function.}

{\selectlanguage{english}
\ \ \ \ If we got all the TCP connections used for the transmission of
the embedded objects, we update the number of page read. We will only
add an event corresponding to the reading time \textbf{Dpc}. If we need
to read another page, the end of the event will take us again to the
function : \textbf{void
srcHTTPSS\_sessionStart(fonctionsHttpssArguments * arg)}.}


\bigskip

{\selectlanguage{english}
\ \ \ \ Otherwise, we update the number of TCP connections which have
ended.}

\clearpage\clearpage\setcounter{page}{1}\pagestyle{Standard}
{\selectlanguage{english}
\ \ Refining\textbf{:}}


\bigskip

{\selectlanguage{english}
An HTTP object has for parameters struct srcHTTPSS:}


\begin{itemize}
\item randomGenerator SM : Size of the main object in a page
\end{itemize}
\begin{itemize}
\item randomGenerator Se : Size of an embedded object in a page
\end{itemize}
\begin{itemize}
\item randomGenerator Nd : Number of embedded objects in a page
\end{itemize}
\begin{itemize}
\item randomGenerator Dpc : Reading time
\end{itemize}
\begin{itemize}
\item randomGenerator Tp : Parsing time for the main page.
\item Int MTU
\item Int nbTCP : number of TCP connections according to the mode ( = 1
in persistant mode)
\item Int nbPage : number of page visited
\item {\selectlanguage{english}
boolean version : True si 1.1, false si 1.0}
\item struct srcHTTPSS\_t * src : source HTTP
\item void * destination : is a pointer to the destination entity for
TCP
\item processPDU\_t destProcessPDU : is the PDU processing function of
the destination
\item double RTTmd : is the Round Trip Time minus transmission time on
the access link
\item int initialWindow : is the initial value of cwnd
\item {\selectlanguage{english}
struct srcTCPSS\_t * srcTCP[4] : TCP sources for burst or persitant
mode, maximum 4 TCP sources}
\item {\selectlanguage{english}
int nbTCPTermine : number of TCP connections which have ended in burst
mode}
\end{itemize}

\bigskip


\bigskip

{\selectlanguage{english}
R0 : Simulate a HTTP session}

{\selectlanguage{french}
R1 : /*\foreignlanguage{english}{Simulate a HTTP session*/}}

{\selectlanguage{english}
\ \ Configure HTTP parameters}

{\selectlanguage{english}
\ \ Launch HTTP session}


\bigskip

{\selectlanguage{english}
R2 :}

{\selectlanguage{english}
\ \ /*Configure HTTP parameters*/}

{\selectlanguage{english}
\ \ \ \ /*Initialise HTTP parameters*/}

{\selectlanguage{english}
\ \ \ \ struct srcHTTPSS\_t * srcHTTPSS\_init(struct randomGenerator\_t
* Sm,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ struct randomGenerator\_t * Se,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ struct randomGenerator\_t * Nd,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ struct randomGenerator\_t * Dpc,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ struct randomGenerator\_t * Tp,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ int MTU, int nbTCP, int version,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ void * destination,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ processPDU\_t destProcessPDU,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ double RTTmd,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ int initialWindow,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ int nbPageMax)\{\ \ }

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ struct srcHTTPSS\_t * result = }

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ (struct srcHTTPSS\_t *) sim\_malloc(sizeof(struct srcHTTPSS\_t
));}


\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ result -{\textgreater} Sm = Sm;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ result -{\textgreater} Se = Se;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ result -{\textgreater} Nd = Nd;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ result -{\textgreater} Dpc = Dpc;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ result -{\textgreater} Tp = Tp;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ result -{\textgreater} MTU = MTU;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ result -{\textgreater} nbTCP = nbTCP; }

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ result -{\textgreater} nbPage = 0;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ result -{\textgreater} version = version;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ result -{\textgreater} destination = destination;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ result -{\textgreater} destProcessPDU = destProcessPDU;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ result -{\textgreater} RTTmd = RTTmd;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ result -{\textgreater} initialWindow = initialWindow;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ result -{\textgreater} nbPageMax = nbPageMax;}


\bigskip


{\selectlanguage{english}
\ \ return result;}

{\selectlanguage{english}
\}}

{\selectlanguage{english}
\ \ \ \ /*Setters*/}

{\selectlanguage{english}
\ \ \ \ struct srcHTTPSS * srcHTTPSS\_setSm(struct randomGenerator\_t *
\ Sm)}

{\selectlanguage{english}
\ \ \ \ struct srcHTTPSS * srcHTTPSS\_setSe(struct randomGenerator\_t[]
* \ Se)}

{\selectlanguage{english}
\ \ \ \ struct srcHTTPSS * srcHTTPSS\_setNd(struct randomGenerator\_t *
\ Nd)}

{\selectlanguage{english}
\ \ \ \ struct srcHTTPSS * srcHTTPSS\_setDpc(struct randomGenerator\_t *
\ Dpc)}

{\selectlanguage{english}
\ \ \ \ struct srcHTTPSS * srcHTTPSS\_setTp(struct randomGenerator\_t *
\ Tp)}

{\selectlanguage{english}
\ \ \ \ struct srcHTTPSS * srcHTTPSS\_setMTU(int MTU)}

{\selectlanguage{english}
\ \ \ \ struct srcHTTPSS * srcHTTPSS\_setversion(boolean \ version)}


\bigskip

{\selectlanguage{english}
\ \ /*Launch HTTP session*/}

{\selectlanguage{english}
\ \ \ \ Start HTTP session}

{\selectlanguage{english}
\ \ \ \ Load Embedded Objects}

{\selectlanguage{english}
\ \ \ \ Load New Page}

\clearpage{\selectlanguage{english}
R3 : /*Simulate a HTTP session*/}


\bigskip

{\selectlanguage{english}
\ \ \ \ /*Configure HTTP parameters*/}

{\selectlanguage{english}
\ \ \ \ \ \ /*Initialise HTTP parameters*/}

{\selectlanguage{english}
\ \ \ \ \ \ /*struct srcHTTPSS * srcHTTPSS\_init({\dots}) \{ {\dots}. \}
*/}


\bigskip


\bigskip

{\selectlanguage{english}
\ \ \ \ /*Launch HTTP session*/}

{\selectlanguage{english}
\ \ \ \ \ \ /*Load the main object trough a single TCP connection and schedule the event end of}

{\selectlanguage{english}
\ \ \ \ \ \ transmission of the main object*/}\linebreak

{\selectlanguage{english}
\ \ \ \ \ \ \textbf{void srcHTTPSS\_sessionStart(}\textbf{void
*}\textbf{ arg)} \{}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ {}-Initialise at 0 the number of TCP connection having ended (it will be used at the end}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ of transmission of the embedded objects.}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ {}-Free the first TCP connection if we are in burst mode and read at least one page}


{\selectlanguage{english}
\ \ \ \ \ \ \ \ {}-Create one single TCP connection in order to send the main object.}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ {}-Send the main object trough the TCP connection. Ge the size of main object by using the}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ random generator of \textbf{Sm.}}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ {}-Add the event end of transmission of the main object. This event will redirect us to}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ the function \textbf{srcHTTPSS\_EOTMainObject} with arg as argument for this function.}

\bigskip


\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ /*The TCP source has sent the main object, so we program need to compute the parsing time, and}

{\selectlanguage{english}
\ \ \ \ \ \ schedule its end in order to send the embedded objects.*/}

{\selectlanguage{english}
\ \ \ \ \ \ \textbf{void srcHTTPSS\_addEOTMainObjet (void * arg)} \{}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ {}-Compute the parsing time of the main object.}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ {}-Schedule the event end of parsing in order to load the embedded objects. This event}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ will take us to the function \textbf{srcHTTPSS\_sendEmbeddedObjects}}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ /*Send the embedded objects after the parsing time.*/}

{\selectlanguage{english}
\ \ \ \ \ \ \textbf{void srcHTTPSS\_sendEmbeddedObjects(void * arg)} \{}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ {}- If burst mode (version == 0) we need to free the TCP connections before creating new}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ ones}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ {}-Create the \textbf{nbTCP} TCP connections}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ Warning \textbf{nbTCP} {\textless} 4}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ {}-Compute the number of embedded objects \textbf{Nd.}}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ {}-Compute the essential number of TCP connections which will be effectively used.}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ If we have \textbf{nbTCP {\textgreater}Nd }, then \textbf{Nd }TCP will be used,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ otherwise all of them will be used.}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ {}-Send the \textbf{Nd }embedded objects on the \textbf{nbTCP }TCP connections.}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ {}-Schedule the event end of transmission of the embedded objects. This event will take us}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ to this function \textbf{srcHTTPSS\_EOTEmbeddedObjects}}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ /*The TCP sources have sent the embedded objects. We need then to schedule the end of the}

{\selectlanguage{english}
\ \ \ \ \ \ reading, and if needed to load a new page after this event.*/}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \textbf{void srcHTTPSS\_EOTEmbbededObjects(}\textbf{void *}\textbf{ arg)} \{}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ If all the TCP connection used have finished their transmission of embedded objects \{}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ {}-Update the number of page read}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ {}-Compute the time of reading of the page \textbf{Dpc}}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ {}-Schedule the event end of reading, and we will read a new page if needed. Which in}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ this later case it will take us to the function \textbf{srcHTTPSS\_sendEmbeddedObjects}}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \} Else \{}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ {}-A TCP connection has ended to send his embedded objects, so we update the number of}


{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ TCP connection having finished}

\pagebreak

\clearpage{\selectlanguage{english}
R4 :}

{\selectlanguage{english}
\ \ /*Configure HTTP parameters*/}

{\selectlanguage{english}
\ \ \ \ /*Initialise HTTP parameters*/}

{\selectlanguage{english}
\ \ \ \ /*struct srcHTTPSS * srcHTTPSS\_init({\dots}) \{ {\dots}. \} */}


\bigskip

{\selectlanguage{english}
\ \ /*Setters*/}

{\selectlanguage{english}
\ \ \ \ /*struct ...*/}


\bigskip

{\selectlanguage{english}
\ \ *Launch HTTP session*/}

{\selectlanguage{english}
\ \ \ \ /*Load the main object trough a single TCP connection and schedule the event end of transmission}

{\selectlanguage{english}
\ \ \ \ of the main object*/}

{\selectlanguage{english}
\ \ \ \ \textbf{void srcHTTPSS\_sessionStart(}\textbf{void *}\textbf{arg)} \{}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ //We cast arg on a HTTP object}

{\selectlanguage{english}
\ \ \ \ \ \ struct srcHTTPSS\_t * src = (struct srcHTTPSS\_t *) arg;}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ /*Initialise at 0 the number of TCP connection having ended (it will be used at the end of}

{\selectlanguage{english}
\ \ \ \ \ \ transmission of the embedded objects.*/}

{\selectlanguage{english}
\ \ \ \ \ \ src-{\textgreater}nbTCPTermine = 0;}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ /*Free the first TCP connection if we are in burst mode and read at least one page*/}

{\selectlanguage{english}
\ \ \ \ \ \ if (src-{\textgreater}nbPage {\textgreater} 0) \{}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ // free the TCP first TCP source}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ srcTCPss\_free(src-{\textgreater}srcTCP[0]);}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ /*Create one single TCP connection in order to send the main object.*/}

{\selectlanguage{english}
\ \ \ \ \ \ src-{\textgreater}srcTCP[0] = srcTCPss\_create(src-{\textgreater}MTU, src-{\textgreater}RTTmd,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ src-{\textgreater}initialWindow,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ src-{\textgreater}destination,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ src-{\textgreater}destProcessPDU);}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ /*Add the event end of transmission of the main object. This event will redirect us to the}

{\selectlanguage{english}
\ \ \ \ \ \ function \textbf{srcHTTPSS\_EOTMainObject} with arg as argument for this function.*/}

{\selectlanguage{english}
\ \ \ \ \ \ srcTCPss\_addEOTEvent(src-{\textgreater}srcTCP[0], event\_create(srcHTTPSS\_EOTMainObject,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ src, 0));}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ /*Send the main object trough the TCP connection. Get the size of main object by using the}

{\selectlanguage{english}
\ \ \ \ \ \ random generator of \textbf{Sm.*/}}

{\selectlanguage{english}
\ \ \ \ \ \ double sm = randomGenerator\_getNextDouble(src-{\textgreater}Sm);}

{\selectlanguage{english}
\ \ \ \ \ \ srcTCPss\_sendFile(src-{\textgreater}srcTCP[0], sm);}

{\selectlanguage{english}
\ \ \ \ \}}

\pagebreak

{\selectlanguage{english}
\ \ \ \ /*The TCP source has sent the main object, so we program need to compute the parsing time, and}

{\selectlanguage{english}
\ \ \ \ schedule its end in order to send the embedded objects.*/}

{\selectlanguage{english}
\ \ \ \ \ \ \textbf{void srcHTTPSS\_addEOTMainObjet (void * arg)} \{}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \ \ //We cast arg on a HTTP object}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ struct srcHTTPSS\_t * src = (struct srcHTTPSS\_t *) arg;}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \ \ /*Compute the parsing time of the main object.*/}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ double tempsParsing = randomGenerator\_getNextDouble(src-{\textgreater}Tp);}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \ \ /*Schedule the event end of parsing in order to load the embedded objects. This event will}


{\selectlanguage{english}
\ \ \ \ \ \ \ \ take us to the function \textbf{srcHTTPSS\_sendEmbeddedObjects*/}}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ event\_add(srcHTTPSS\_sendEmbeddedObjects, src, motSim\_getCurrentTime() + tempsParsing);}

\pagebreak

{\selectlanguage{english}
\ \ \ \ /*Send the embedded objects after the parsing time.*/}

{\selectlanguage{english}
\ \ \ \ \ \ \textbf{void srcHTTPSS\_sendEmbeddedObjects(void * arg)} \{}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \ \ //We cast arg on a HTTP object}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ struct srcHTTPSS\_t * src = (struct srcHTTPSS\_t *) arg;}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \ \ int i;}


\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \ \ /*If burst mode (version == 0) we need to free the TCP connections before creating new}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ ones*/}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ if (src-{\textgreater}version == 0) \{}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ for ( i=0; i {\textless} src-{\textgreater}nbTCP; i++) }

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \{}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ if (src-{\textgreater}nbPage {\textgreater} 0) \{}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ srcTCPss\_free(src-{\textgreater}srcTCP[i]);}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ \}}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ /*Create the \textbf{nbTCP} TCP connections}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ Warning \textbf{nbTCP} {\textless} 4 according to the model*/}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ src-{\textgreater}srcTCP[i] = srcTCPss\_create(src-{\textgreater}MTU,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ src-{\textgreater}RTTmd, src-{\textgreater}initialWindow,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ src-{\textgreater}destination, src-{\textgreater}destProcessPDU);}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \ \ /*Compute the number of embedded objects \textbf{Nd.*/}}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ int Nd = randomGenerator\_TruncParetoGetNext(src-{\textgreater}Nd);}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \ \ /*Compute the essential number of TCP connections which will be effectivly used.}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ If we have \textbf{nbTCP {\textgreater}Nd }, then \textbf{Nd }TCP will be used,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ otherwise all of them will be used.*/}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ int fin;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ if (src-{\textgreater}nbTCP {\textgreater} Nd) \{}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ fin = Nd;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ src-{\textgreater}nbTCPTermine = src-{\textgreater}nbTCPTermine +}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ src-{\textgreater}nbTCP - Nd;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \} else \{}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ fin = src-{\textgreater}nbTCP;}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \ \ /*Send the \textbf{Nd }embedded objects on the \textbf{nbTCP }TCP connections.*/}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ for (i = 0; i{\textless}Nd; i++) }

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ //Compute the size of an embedded object}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ double s = randomGenerator\_getNextDouble(src-{\textgreater}Se);}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ int sizeEbOb = (int) s;}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ /*We send the i-th embedded object on the \textbf{i modulo nbTCP th }TCP connection.}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ For example if we have 3 TCP connections and 5 embedded objects, we send the first}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ embedded object on the first TCP connection, the second object on the second TCP}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ connection. The third object on the third TCP connection. The fourth object on the}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ first TCP connection and the fith object on the second TCP connection.*/}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ srcTCPss\_sendFile(src-{\textgreater}srcTCP[i\%(src-{\textgreater}nbTCP)], s);}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \ \ /*Schedule the event end of transmission of the embedded objects. This event will take us

{\selectlanguage{english}
\ \ \ \ \ \ \ \ to this function textbf{srcHTTPSS\_EOTEmbeddedObjects*/}}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ for (i = 0; i{\textless}fin; i++) \{}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ //Launch the end of transmission of a single TCP connection}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ srcTCPss\_addEOTEvent(src-{\textgreater}srcTCP[i], event\_create(srcHTTPSS}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ EOTEmbeddedObjects, src,0));}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ // !!! If sendFile of TCP has already finished, we will wake him up in order the event}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ can be scheduled.}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ srcTCPss\_wakeUp(src-{\textgreater}srcTCP[i]);}

\pagebreak

{\selectlanguage{french}
\ \ \ \ /*The TCP sources have sent the embedded objects. We need then to schedule the end of the reading,}

{\selectlanguage{french}
\ \ \ \ and if needed to load a new page after this event.*/}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \textbf{void srcHTTPSS\_EOTEmbbededObjects(}\textbf{void *}\textbf{ arg)} \{}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \ \ /*A TCP connection has ended to send his embedded objects, so we update the number of TCP}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ connection having finished*/}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ src-{\textgreater}nbTCPTermine++;}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \ \ /*If all the TCP connection used have finished their transmission of embedded objects*/}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ if (src-{\textgreater}nbTCPTermine == src-{\textgreater}nbTCP) \{}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ /*Update the number of page read*/}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ src-{\textgreater}nbPage++;}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ /*Compute the time of reading of the page \textbf{Dpc*/}}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ double tempsReading = randomGenerator\_getNextDouble(src-{\textgreater}Dpc);}

\bigskip

{\selectlanguage{english}
\ \ \ \ \ \ \ \ /*Schedule the event end of reading, and we will read a new page if needed. Which in this}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ later case it will take us to the function \textbf{srcHTTPSS\_sendEmbeddedObjects*/}}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ if (src-{\textgreater}nbPage {\textless} src-{\textgreater}nbPageMax) \{}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ event\_add(srcHTTPSS\_sessionStart, src,}

{\selectlanguage{english}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ motSim\_getCurrentTime()+ tempsReading);}
\end{document}
