\documentclass{book}
\usepackage{xr}
\externaldocument{random-generator-en.tex}
\usepackage{amsmath}
\usepackage[utf8x]{inputenc}
\usepackage[french]{babel}
\usepackage{graphicx}
\usepackage{srcltx}
\usepackage{listings}
\usepackage[pdftex]{thumbpdf}
\usepackage[pdftex,colorlinks]{hyperref}
\usepackage{index}
\usepackage{hyperref}


\title{Network Discrete Event Simulator}

\author{Emmanuel Chaput}

\makeindex

\begin{document}
\maketitle

%\begin{abstract}
   
    {\em Network Discrete Event Simulator} (or {\sc ndes}) is one
library which permits the creation of network discrete event simulators. This  document is a user guide and a programmer guide for this utility.

   {\sc Ndes} was basically designed to simulate a
specific scenario (scheduling of packets on a DVB-S2 link). 
But it also includes various portions of code with whom
the author had other goals. Its use in a different context is however very difficult, especially because of the absence of a substantial library of models.

%\end{abstract}

\newpage
\tableofcontents
\newpage

%========================================================================
%
%========================================================================
\chapter{User's manual}

\input{introduction-generale-en}
\input{tutoriel-utilisateur-en}
%\input{exemples-utilisateur-en}

%========================================================================
%
%========================================================================
\chapter{Programmer's manual}

%\input{architecture-en}
\input{tutoriel-programmeur-en}
%\input{motsim-en}
%\input{ndes-object-en}
%\input{log-en}

\chapter{Traffic models}
\input{httpmodel-en}
%========================================================================
%
%========================================================================


\chapter{The library}

%\input{sondes-en}
\input{random-generator-en}
%\input{date-generator-en}
%\input{pdu-en}
%\input{file-pdu-en}
%\input{srv-gen-en}
%\input{pdu-sink-en}
%\input{link-simplex-en}
%\input{dvbs2link-en}
%\input{sched-acm-en}
%\input{sched-acm-knapsack-en}


\section{GnuPlot diagrams}
\label{section:gnuplot}

%========================================================================
%
%========================================================================

\section{Notion of simulation and of campaign}

A simulation is a single instance of an execution of an event sequence
following the initialization of the model. A campaign is a
result of simulations on the same model with a reset of
variables between two simulations.

    The sensors relating to the simulation are re-initialized at the end of the
simulation. Probes may be related to the campaign; they will not be reseted at the end of the campaign and they can allow also inter-simulation values​​, for example confidence intervals.

%========================================================================
%
%========================================================================
%========================================================================
%
%========================================================================
\chapter{Annexes}

\section{Function index}

\printindex

\end{document}
